Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2018-06-12 inst/examples/20160715-Krakow-Fennica.Rmd

**Open source** fully transparent and reproducible data analytics: https://github.com/rOpenGov/fennica

@@

- \textcolor{blue}{https://github.com/rOpenGov/fennica}

>>>>

**Open source** fully transparent and reproducible data analytics: https://github.com/COMHIS/fennica

@@

- \textcolor{blue}{https://github.com/COMHIS/fennica}

### 2018-06-12 inst/examples/notebook.Rmd

```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png

@@

```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
catalogue <- "Fennica"

>>>>

```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
# https://github.com/COMHIS/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png

@@

```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
# https://github.com/COMHIS/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
catalogue <- "Fennica"
